---
name: Medha
surname: Khanal
position: "Marketing Analytics & Digital Marketing Student"
phone: "+1 (562) 330-8335"
www: "ilyakhl313-prog.github.io/Medha-Portfolio"
email: "ilyakhl313@gmail.com"
github: "ilyakhl313-prog"
linkedin: "medha-khanal"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(tibble)
```

# Professional Summary

Culturally adept International Business and Marketing student at Cal Poly Pomona with experience in digital marketing, campaign strategy, and analytics. Skilled in SEO, Google Ads, and social media campaigns, with hands-on experience analyzing performance through Google Analytics simulations. Proven ability to collaborate across diverse teams, contribute to marketing initiatives, and translate data into actionable business insights.

# Technical Skills

- **Web Technologies:** HTML, Quarto, Google Analytics, etc.
- **Marketing:** Digital Marketing Strategy, Social Media Campaigns, Branding, E-commerce (Shopify), Influencer Marketing
- **Analytics:** SEO Keyword Research, A/B Testing, Campaign Analysis, Sponsorship & Market Research
- **Tools:** Google Ads, Google Analytics, R, Microsoft Excel
- **Professional:** Communication, Collaboration, Leadership, Public Speaking, Cross-Cultural Skills

# Education

```{r}

tribble(
  ~Degree, ~Year, ~College, ~Institution,
  "B.S. International Business & Marketing (Senior)", "Aug 2023 – Present", "College of Business Administration", "California State Polytechnic University, Pomona"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Work Experience

```{r}
tribble(
  ~Years, ~Company, ~Duties, ~Title,

  "March 2025 – August 2025", "Walt Disney Parks and Resorts (Disney College Program)",
  list(
    "Participated in professional development courses covering financial analysis, company history, culture, and technology.",
    "Collaborated with diverse international teams on company projects and events.",
    "Supported Disney banquet events by assisting with planning and guest services.",
    "Demonstrated strong cross-cultural communication and teamwork in a fast-paced environment."
  ),
  "Disney College Program Intern",

  "August 2024 – December 2024", "Global Career Accelerator",
  list(
    "Designed and built a functional e-commerce website using Shopify.",
    "Conducted keyword research and applied SEO strategies to improve search engine visibility.",
    "Created and managed paid and organic social media content for Instagram and Facebook.",
    "Developed and launched a paid search campaign using Google Ads, focusing on performance optimization."
  ),
  "Digital Marketing Trainee",

  "August 2024 – December 2024", "CLD PR",
  list(
    "Collaborated with a global PR team to execute marketing and branding initiatives.",
    "Sourced influencers and assisted in planning influencer marketing campaigns.",
    "Conducted sponsorship research and managed brand outreach for events.",
    "Maintained and tracked clothing inventory using an organized system."
  ),
  "Fashion PR Intern"

) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```